---
title: "README"
output: 
  github_document:
    toc: yes
---



# Sweet Summer Child Score

Sweet Summer Child Score (SSCS) is a scoring mechanism for latent risk. It will help you quickly and efficiently scan for the possibility of harm to people and communities by a socio-technical system. This package is an R version of Python code found at: https://github.com/summerscope/summerchildpy

# Run Summer Summer Child app to assess the risk of your socio-technical system

How it looks like when you run it.

```{r echo=FALSE,message=FALSE,fig.width=5,fig.height=5,fig.align='center',cache=TRUE}
library(png)
library(grid)
img <- readPNG("data-raw/app.png")
grid.raster(img)
```


## 1. From RStudio

**Install and load the R package**

```{r eval=FALSE}
if(!require(devtools,quietly = TRUE))
  install.packages("devtools")
devtools::install_github("summerscope/summerchildr")
library(summerchildr)
```

**Run the app**

```{r eval=FALSE}
shiny::runApp(runSummerChildApp())
```


## 2. From the terminal

Run the following code in a terminal window - **Requires R (>= 2.10) to be installed**

```
R -e "devtools::install_github('summerscope/summer-child-r', force = TRUE);library(summerchildr); shiny::runApp(runSummerChildApp())"
```

Click on the `http` link that appears in the terminal.

## FAQ: If you're having issues with R packages installation

1. Clone the repository

```
git clone git@github.com:summerscope/summerchildr.git
cd summerchildr
```

2. Run the app in the terminal after restoring the environment:

```
R -e "renv::restore(); library(summerchildr); shiny::runApp(runSummerChildApp())"
```

The same commands in the chunk above can be run in R Studio to restore the environment before running the app.
