---
title: "README"
output: 
  github_document:
    toc: yes
---

# Sweet Summer Child Score

Sweet Summer Child Score (SSCS) is a scoring mechanism for latent risk. It will help you quickly and efficiently scan for the possibility of harm to people and communities by a socio-technical system. This package is an R version of Python code found at: https://github.com/summerscope/summerchildpy

# Run Summer Summer Child app to assess the risk of your socio-technical system

## 1. From RStudio

**Install and load the R package**

```{r eval=FALSE}
if(!require(devtools,quietly = TRUE))
  install.packages("devtools")
devtools::install_github("summerscope/summerchildr")
library(summerchildr)
```

**Run the app**

```{r eval=FALSE}
shiny::runApp(runSummerChildApp())
```


## 2. From the terminal

Clone this repository and change directory to repository folder.

```
git clone git@github.com:summerscope/summerchildr.git
cd summerchildr
```

Run the app

```
make run
```

Click the `http` link that appears in the terminal.
